Password file disclosures are a frequent problem for many companies, which
makes their users the target of identify theft and similar attacks.   
This work provides a new general cryptographic technique to prevent an
attacker from efficiently cracking individual passwords from a stolen
password database.   PolyPasswordHasher employs a threshold cryptosystem to protect
password hashes so that they cannot be verified unless a threshold of them
are known.   (This is conceptually similar to encrypting the passwords with a 
key that is only recoverable when a threshold of passwords are known.)
%PolyPasswordHasher obscures password hash data 
%passwords may not be cracked
%the effort an attacker must employ to crack passwords.
%protecting password data from an attacker.   With our system PolyPasswordHasher,
%an attacker must simultaneously crack multiple passwords
%In this work, we apply PolyHashing to the problem of password verification and 
%storage to build a system called PolyPasswordHasher. % PolyPasswordHasher prevents 
%efficient password cracking in the event of a password file disclosure.  
Even if the password file and all other data on disk is obtained by a 
malicious party, the attacker cannot crack any individual password without 
simultaneously guessing a large number of them correctly.   PolyPasswordHasher
is the first single server, software-only technique that increases
the attacker's search space exponentially.   The result is that even cracking 
small numbers of weak passwords is infeasible for an attacker.   

%For sufficiently 
%strong passwords, PolyPasswordHasher will even provide information theoretic 
%security, making password cracking impossible.  
PolyPasswordHasher achieves these properties with similar efficiency, storage,
and memory requirements to existing salted hash schemes,
%performance.
%PolyPasswordHasher requires comparable storage to the current best practice salted 
%secure hashing scheme, requiring a total of about 1KB of additional memory 
%(with no additional per account cost) and no more than 1 extra byte of disk 
%space per account.
%Our implementation of PolyPasswordHasher is similar
%in speed to existing salted hash schemes, 
performing
tens of thousands of account authentications per second.    
When using the current best practice (of salting and hashing), 
cracking three passwords that are comprised of 6 random characters on
a modern laptop would take under a hour.  However, when protected with
PolyPasswordHasher, cracking these passwords when using every computer in existence
would take longer than the estimated age of the universe.
%\cappos{Not the strongest thing to end on.   Consider talking about exponential
%increase in time last.}
